---
title: "Cabbages"
author: "Nathaly Ruiz"
date: "2024 Fall Semester"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```


# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  


$H_0$: There is no difference in the average VitC between both. of the cultivation methods. 
$H_A$: There is a difference in the average VitC betweenboth of the cultivation methods

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

vitC  ~ cultivation method

vitC is numerical

cultivation is categorical

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question





### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
The grapph shows that c52 is higher in vitamin c than c39.

```{r}
favstats(VitC~Cult,data=veggy)
```
The table shows the cultivation method c52 has a higher vitamin c content than
c39. C52 shows an average difference of about 13 mg.
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(VitC~Cult,data=veggy)
```
The p-value, 0.0000000003405, I reject the null hypothesis, concluding that there is a vitamin c difference in the cultivation methods of c52 and c59

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

It appears from the boxplot that cultivation method c52 results in higher vitamin C content. The numerical summary shows that on average c52 results in about 13 vitamn c units more. The P-Value is 3.405e-08 which is less than 0.05, so the null hypothesis is extremely unlikely; so we reject the null hypothesis. We conclude there is a difference on vitamin c content based on cultivation.
